%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Indie Game} % Type
    {Lost in Peril} % Name
    {Java} % Language
    {2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
         \item {This began as a project that was created to fulfill requirements for the classes Software Engineering One and Two}
         \item {Fueled by the Java based game engine, LibGDX, this is a working product that lets a user have an entertaining and exciting              experience.}
         \item {This product is still being developed to this day, and has      features that include controller support and being available on         Google Play.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Thesis} % Type
    {WebRTC} % Name
    {HTML5 and JavaScript} % Language
    {2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {This was an exit option to achieve my Master's Degree
        through research and development upon WebRTC API security flaws.}
        \item {Through research and surveys, security flaws with WebRTC API were mitigated.}
        \item {This involved documenting these security issues, creating a      prototype that mitigates said issues, and then writing a thesis.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {School Project} % Type
    {Web Service Radio Station} % Name
    {LAMP Stack} % Language
    {2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A project that used Linux, Apache, MySQL, PHP, HTML5, JavaScript and Angular to provide a great learning experience using high-demand     technologies and languages.}
        \item {An AngularJS development that created a simple webpage, and      implemented a web radio.}
      \end{cvitems}
    }
    
%----------------------------------------------------------
  \cventry
    {School Project} % Type
    {Distributed Hash Table} % Name
    {C/C+} % Language
    {2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A project that created a full implementation of a Distributed Hash Table which created N-random nodes 
        with each having a 30 percent change of being online, their corresponding lookup table, and performed 5 random look ups.}
        \item {Wrote using C/C++, and then expanded upon using GraphStream for a visual representation.}
        \item {YouTube Link: }
      \end{cvitems}
    }
    
%----------------------------------------------------------
\end{cventries}